03_wrangle

### 2020-08-21 analysis/03_datawrangling.Rmd
now with fewer DEGs

@@

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)
```

>>>>

### manipuluation

```{r}
head(allDEG)

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 )
dim(allDEG)
dim(filteredDEGs)

makemanipulationDEGtables <- function(whichcomparisons){
  df <- filteredDEGs %>%
    filter(comparison %in% whichcomparisons) %>%
     mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G"),
         group = paste(sex, tissue, sep = "")) %>%
  mutate(res = paste("(", posneg, ")", sep = "")) %>%
  mutate(compres = paste(comparison, res, sep = "")) %>%
  select(gene, group, compres) %>%
  group_by(group,gene) %>%
  summarize(results = str_c(compres, collapse = "; ")) %>%
  mutate(n = (str_count(results, pattern = ";"))+1) %>%
  arrange(desc(n))  %>%
  filter(n>1) %>%
  group_by(group,results) %>%
  summarize(genes = str_c(gene, collapse = "; "))  %>%
  #arrange(group, results) %>%
  mutate(n = (str_count(genes, pattern = ";"))+1) %>%
  arrange(desc(n))
  print(head(df))
return(df) 
}

removalcomps <- c("inc.d3_m.inc.d3", "inc.d9_m.inc.d9", "inc.d17_m.inc.d17", "hatch_m.n2")
early <- c("early_inc.d9", "hatch_early")
late <- c("hatch_prolong", "inc.d17_prolong")

removalDEGs <- makemanipulationDEGtables(removalcomps)
hatchDEGs <- makemanipulationDEGtables(early)
prolongDEGs <- makemanipulationDEGtables(late)

manipDEGs <- rbind(removalDEGs, hatchDEGs) %>%
  rbind(., prolongDEGs) %>%
  arrange(desc(n))
head(manipDEGs)
```

@@

```{r write}
write.csv(allDEG, "../results/03_allDEG.csv", row.names = F)
write.csv(candidatevsd, "../results/03_candidatevsd.csv")
write.csv(wideDEGsSequential, "../results/table1.csv", row.names = F)

write.csv(removalDEGs, "../results/removalDEGs.csv")
write.csv(hatchDEGs, "../results/hatchDEGs.csv")
write.csv(prolongDEGs, "../results/prolongDEGs.csv")

write.csv(manipDEGs, "../results/manipDEGs.csv")
